---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
suppressMessages(library(rhymer))
```

# rhymer
[![Build Status](https://travis-ci.org/landesbergn/rhymer.svg?branch=master)](https://travis-ci.org/landesbergn/rhymer)
[![Coverage Status](https://img.shields.io/codecov/c/github/landesbergn/rhymer/master.svg)](https://codecov.io/github/landesbergn/rhymer?branch=master)

### Overview
The goal of `rhymer` is to get rhyming and other related words through the [Datamuse API](http://www.datamuse.com/api/). This package includes basic functions to get rhymes and other similar words based on meaning, spelling, or sound.  

## Installation

You can install rhymer from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("landesbergn/rhymer")
```

## Example
They say nothing rhymes with _orange_...

```{r example1}
get_rhyme("orange", return_type = "word")
```

Feeling down? How about this cloud of words with similar meaning to _happy_:

```{r example2}
word_data <- get_means_like("happy", return_type = "df")
wordcloud::wordcloud(words = word_data$word, 
                     freq = word_data$score, 
                     colors = c("lightsteelblue1","lightsteelblue2","lightsteelblue3","lightsteelblue"))
```

Eminem wrote the classic rap song ['Lose Yourself'](https://genius.com/Eminem-lose-yourself-lyrics), but could it be better with `rhymer`?

```{r}
glue::glue("
  His palms are sweaty
  Knees weak arms are {get_rhyme('sweaty', return_type = 'word', num_syl = 2)}

  There's vomit on his sweater already
  Mom's {get_rhyme('already', return_type = 'word', num_syl = 3)}
")
```
  
## Main functions
`rhymer` has 4 main functions that allow you to get data on related words through the Datamuse API.    
  
They are: 

  - `get_rhyme` - a function to get rhyming words  
  - `get_means_like` - a function to get words with similar meaning  
  - `get_sounds_like` - a function to get words that sound similar  
  - `get_spelled_like` - a function to get words that are spelled similarly  

There is also a more flexible function `get_other_related` that allows you to use the API to get data on other related words using a series of 'codes' described on the [Datamuse API website](http://www.datamuse.com/api/).  

Each function takes the basic arguments of:  
  - `word` the word to base results on  
  - `return_type` what type of data return (options are _df_ for a data frame, _vector_ for a vector, _word_ for a single word, and _random\_word_ for a random word)  
  - `limit` max number of related words to return  
  
(`get_rhyme` also has a special helper for the number of syllables to return called `num_syl`)