---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rhymer

The goal of rhymer is to get rhyming and other related words through the [Datamuse API](http://www.datamuse.com/api/).

## Installation

You can install rhymer from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("landesbergn/rhymer")
```

## Example
They say nothing rhymes with _orange_...

```{r example}
library(rhymer)

get_rhyme("orange")
```

## Main functions
`rhymer` has 4 main functions that allow you to get data on related words through the datamuse API.    
  
They are: 

  - `get_rhyme` - a function to get rhyming words  
  - `get_means_like` - a function to get words with similar meaning  
  - `get_sounds_like` - a function to get words that sound similar  
  - `get_spelled_like` - a function to get words that are spelt similarly  

There is also a more flexible function `get_other_related` that allows you to use the API to get data on other related words using a series of 'codes' described on the (datamuse API website)[http://www.datamuse.com/api/].  
