---
title: "Intro to rhymer"
author: "Noah Landesberg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Welcome to `rhymer`, an R package for getting rhyming and other related words through the datamuse API. I highly recomend reading through the datamuse API [website](http://www.datamuse.com/api/) before getting started.

## Main functions
`rhymer` has 4 main functions that allow you to get data on related words through the datamuse API.    
  
They are: 

  - `get_rhyme` - a function to get rhyming words  
  - `get_means_like` - a function to get words with similar meaning  
  - `get_sounds_like` - a function to get words that sound similar  
  - `get_spelled_like` - a function to get words that are spelt similarly  

There is also a more flexible function `get_other_related` that allows you to use the API to get data on other related words using a series of 'codes' described on the [datamuse API website](http://www.datamuse.com/api/).  

Each function is default limited to a maximum of 10 results, but can return more. A function call will return a dataframe with a row for each word, and an associated score. Different functions will return slightly different additional columns.

```{r}
library(rhymer)
```


```{r}
# For example, get_rhyme or get_sounds_like returns the additional column numSyllables
rhymer::get_rhyme("test")
rhymer::get_sounds_like("test")

# and get_means_like returns tags specifying the part of speach
rhymer::get_means_like("test")
```
